\documentclass[dissertation]{aaltoseries}
%\documentclass[dissertation,draft*]{aaltoseries}
%\documentclass[draft]{aaltoseries}
%\usepackage{aaltothesis}
\usepackage[utf8]{inputenc}
%\usepackage[utf8]{fontenc}
%\usepackage{pslatex}
%\usepackage{ae,aecompl}
\usepackage[T1]{fontenc}
\usepackage[finnish,english]{babel}
\usepackage{lipsum}
%\usepackage{auto-pst-pdf}
%\usepackage{amssymb}
%\usepackage{amsmath}
\usepackage{url}
\usepackage{psfrag,color,pstricks,pst-grad}
\usepackage[normalem]{ulem}
%\usepackage{graphicx}
%\usepackage[pdftex]{graphicx}
%\usepackage{lipsum}% just to automatically generate text
\usepackage{amsmath,amsfonts,amssymb,amsbsy}  
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{upgreek}
\usepackage{siunitx}
\usepackage{tabularx}
%\usepackage{setspace}
%\doublespacing
\newcommand{\ud}{\mathrm{d}}
\newcommand{\bb}{\mathbf}
\newcommand{\ca}{\mathcal}

\hyphenation{macro-scale nano-scale damped}

\newcommand{\fb}{\left[f_B(\omega,T)+\frac{1}{2} \right]}
\newcommand{\fbbg}{\left[f_B(\omega,\Tenv)+\frac{1}{2} \right]}
\newcommand{\fbi}{\left[f_B(\omega,T_{i})+\frac{1}{2} \right]}
\newcommand{\fbj}{\left[f_B(\omega,T_{j})+\frac{1}{2} \right]}
\newcommand{\mbb}{\mathbb}
\newcommand{\gem}{\mathbb{G}}
\newcommand{\gems}{\mathbb{g}}
\newcommand{\bu}{\bb{u}}
\newcommand{\bd}{\bb{d}}
\newcommand{\bE}{\bb{E}}
\newcommand{\br}{\bb{r}}
\newcommand{\bp}{\bb{p}}
\newcommand{\bG}{\bb{G}}
\newcommand{\Pfluc}{\bb{P}_{\textrm{fluc}}}
\newcommand{\pom}{(\omega)}
\newcommand{\epsenv}{\varepsilon_{\textrm{env}}}
\newcommand{\Tenv}{T_{\textrm{env}}}
\newcommand{\Eenv}{\bb{E}_{\textrm{env}}}
\newcommand{\Eenvhat}{\hat{\bb{E}}_{\textrm{env}}}
\newcommand{\Eenvtilde}{\tilde{\bb{E}}_{\textrm{env}}}
\newcommand{\gemfull}{{\gem}^{\textrm{CM}}}
\newcommand{\tildegemfull}{{\gem}^{\textrm{full}}}
\newcommand{\kw}{k_0}
\newcommand{\unitdyadic}{\bb{I}_{3 \times 3}}
\newcommand{\change}{\uline}
%\newcommand{\change}{}
\newcommand{\listofsymbols}{%
  \chapter*{Symbols and abbreviations}%
}


% The author of the dissertation
\author{Kimmo S\"a\"askilahti}
% The title of the thesis


\title{Computational modeling and spectral\\ analysis of nanoscale energy transfer}

\begin{document}
% \doublespace
\pagenumbering{roman}

\draftabstract{Swift progress in the synthesis and processing of materials with nanoscale feature sizes has spawned new possibilities to control the flow of thermal energy. New materials and devices with engineered thermal properties are expected to enable, e.g., clean and more efficient production of energy from waste heat by thermoelectric converters, reducing the energy consumption of digital electronics, and generating novel technologies such as heat-assisted magnetic recording and phase-change memories. As the classical laws of energy transfer do not generally apply in nanoscale, practical realization of such applications calls for powerful computational methods delivering scientific understanding of nanoscale heat transfer.

The goal of this thesis is to develop new computational models and methods for describing energy transfer in atomic-scale structures and to apply the methods to generate useful insight into various thermal phenomena. The work is founded on classical molecular dynamics simulations and quantum-mechanical Green's function approaches, both using the fluctuation-dissipation theorem to couple the studied systems to external heat baths. To enable detailed analysis of energy transfer mechanisms in thermal conduction, new methods to spectrally decompose the lattice heat current into frequency components are also developed. Spectral analysis is applied in the thesis to identify non-linear energy transfer mechanisms at material interfaces and to determine the mean free paths of heat carriers in carbon nanotubes. The results also suggest that the thermoelectric efficiency of silicon nanowires can be increased by a specific superlattice structure and that the electromagnetic energy transfer rate between dielectric nanoparticles can be tuned by a mirror cavity.

In addition, the thesis initiates the development of a unified fluctuational model for describing energy transfer by lattice vibrations, electromagnetic fields, and electrons in a single mathematical framework that can generate extensive understanding of the energy conversion phenomena present in small structures. As a whole, the methods and results of the thesis provide new analytical and numerical tools for describing nanoscale energy transfer within a framework that may, with further development, become instrumental also in modeling energy conversion and transfer processes in multiscale systems involving heat, light and electricity.}

\draftabstract[finnish]{Nanoteknologian nopea kehitys on synnytt\"anyt uusia tapoja hallita l\"amp\"oenergiaa. L\"amp\"oenergian tehokkaan hallinnan ja ohjauksen odotetaan mahdollistavan mm. puhtaan energiantuotannon termos\"ahk\"oisill\"a materiaaleilla, digitaalielektroniikan tehonkulutuksen pienent\"amisen sek\"a t\"aysin uusien sovellusten kuten l\"amp\"oohjatun magneettisen tallentamisen kehitt\"amisen. L\"amp\"oenergiaa hy\"odynt\"avien sovellusten kehitt\"aminen vaatii kuitenkin erinomaista ymm\"arryst\"a energiansiirtomekanismeista hyvin pieniss\"a rakenteissa.

V\"ait\"oskirjaty\"on tavoitteena on kehitt\"a\"a uusia laskennallisia malleja ja menetelmi\"a l\"amm\"onsiirron mallintamiseen nanomittakaavan rakenteissa sek\"a soveltaa menetelmi\"a uuden ymm\"arryksen synnytt\"amiseen. Ty\"o perustuu klassiseen ep\"atasapainotilan molekyylidynamiikkamenetelm\"a\"an sek\"a kvanttimekaanisiin Greenin funktio -laskuihin, jotka molemmat hy\"odynt\"av\"at fluktuaatio-dissipaatioteoriaa tarkasteltavan systeemin ja ymp\"arist\"on v\"alisen kytkenn\"an kuvaamiseen. L\"amm\"onjohtumismekanismien analysoimiseksi kehitet\"a\"an mm. menetelm\"a hilav\"ar\"ahtelyjen kuljettaman l\"amp\"ovirran jakamiseksi taajuuskomponentteihin. Ty\"on malleja ja spektraalista hajotelmaa sovelletaan ep\"alineaaristen l\"amm\"onsiirtomekanismien tunnistamiseen materiaalirajapinnoilla sek\"a l\"amp\"o\"a kuljettavien hilav\"ar\"ahtelyjen sirontapituuksien m\"a\"aritt\"amiseen hiilinanoputkissa. Ty\"on tulokset osoittavat my\"os, ett\"a piinanolankojen termos\"ahk\"oisi\"a ominaisuuksia voidaan parantaa erityisell\"a superhilarakenteella ja ett\"a s\"ahk\"omagneettisen l\"amm\"onsiirron voimakkuutta nanopartikkeleiden v\"alill\"a voidaan muokata sijoittamalla partikkelit peilikaviteettiin.

Ty\"oss\"a kehitet\"a\"an lis\"aksi yhten\"ainen matemaattinen malli hilav\"ar\"ahtelyjen, s\"ahk\"omagneettisten kenttien ja elektronien l\"amm\"onkuljetuksen mallintamiseen. Kokonaisuudessaan v\"ait\"oskirjaty\"o tarjoaa energiansiirron mallintamiseen ty\"okaluja, jotka voivat tulevaisuudessa olla merkitt\"av\"ass\"a roolissa valon, s\"ahk\"on ja l\"amm\"on vuorovaikutuksien kuvaamisessa eri mittakaavan rakenteissa.}

% 

\author{Kimmo S\"a\"askilahti}
\begin{preface}[Espoo, Finland]
Preface text
\end{preface}

\vspace{1cm}
\noindent
\textit{Funding organizations, computational resources}

\tableofcontents

\listofpublications

\chapter*{Summary of article contents}
\addcontentsline{toc}{chapter}{Summary of article contents}

\textbf{Publication I} investigates the role of anharmonic phonon scattering in thermal conduction across planar material interfaces and provides the first application of the spectral decomposition formula for heat current. The results show that anharmonic phonon scattering facilitates thermal conduction across the interface by providing a dissipation mechanism for evanescent waves and by enabling multi-phonon energy transfer processes at the interface.

\vspace{1cm}
\noindent
\textbf{Publication II} presents a new method for determining the frequency-dependent phonon mean free paths from non-equilibrium simulations. The determined mean free paths directly reflect the decay of heat current in non-equilibrium, allowing for straightforwardly assessing the contributions of different vibrational frequencies to thermal conduction in tubes of different lengths. Room-temperature mean free paths in carbon nanotubes are shown to exceed 10 $\upmu$m at low frequencies, highlighting their extraordinary thermal properties with applications in, e.g., thermal management of electronics. 

\vspace{1cm}
\noindent
\textbf{Publication III} presents the first study of the effect of periodic twinning stacking faults on the thermal conductivity of silicon nanowires. Molecular dynamics simulations show that the nanowire thermal conductivity can be notably reduced by the periodic twinning, suggesting the possibility to increase the thermoelectric efficiency by such superlattice structures.

\vspace{1cm}
\noindent
\textbf{Publications IV, V} and \textbf{VI} focus on thermal conduction in nanoscale point contacts. Simulations for point contacts in a two-dimensional square lattice reveal interference patterns in local temperature profiles, not captured by Fourier's law. Quantum statistics are shown to modify temperature profiles in point contacts at low temperatures, but the effect is shown to be weak for graphene at room temperature.

\vspace{1cm}
\noindent
\textbf{Publication VII} presents Langevin theory of electromagnetic energy transfer, providing an alternative description complementing the traditional fluctuational electrodynamics. Numerical results for nanoparticles in a mirror cavity demonstrate the possibility to tune the rate of electromagnetic energy transfer between dielectric bodies by an inhomogeneous environment, in analogy to the well-known Purcell effect enabling the tuning of spontaneous emission.

\chapter*{Author's contribution}
\addcontentsline{toc}{chapter}{Author's contribution}
The author wrote the first draft, developed and/or adapted the required theoretical and numerical models and performed all the calculations and numerical analysis in \textbf{Publications I, II, IV, V, VI}, and \textbf{VII}.

\vspace{1cm}
\noindent
The author actively contributed to the writing of the manuscript and participated in the interpretation of numerical results in \textbf{Publication III}.

\listofsymbols
\addcontentsline{toc}{chapter}{Symbols and abbreviations}
\setlist[description]{style=multiline,topsep=10pt,leftmargin=3cm,font=\normalfont\normalfont\space,align=parleft}

\begin{description} \itemsep2pt
  \item[$\alpha^{\textrm{CM}}$] Clausius-Mossotti polarizability
  \item[$c$] Electron annihilation operator 
  \item[$c^{\dagger}$] Electron creation operator 
  \item[$C$] Position autocorrelation function
  \item[$d$] Dipolar displacement 
  \item[$\delta_{ij}$] Kronecker delta
   \item[$\delta(x-x')$] Dirac delta function
  \item[$\Delta T$] Temperature difference
  \item[$D$] Nanowire diameter
    \item[$e$] Local vibrational energy
   \item[$E$] Electric field  
   \item[$E_{\textrm{env}}$] Background electric field
   \item[$\varepsilon$] Electric permittivity
   \item[$\varepsilon_0$] Vacuum permittivity
   \item[$\varepsilon_{\textrm{env}}$] Electric permittivity of the environment
   \item[$\eta$] Electron Langevin noise operator
   \item[$f$] Frequency
   \item[$f_{\textrm{BE}}$] Bose-Einstein function
   \item[$f_{\textrm{FD}}$] Fermi-Dirac function
  \item[$F$] Force
   \item[FDT] Fluctuation-dissipation theorem
  \item[$g$] Spectrally decomposed thermal conductance
  \item[$G$] Green's function matrix
  \item[$\mathbb{G}$] Electromagnetic Green's dyadic
  \item[GF] Green's function 
  \item[$\gamma$] Langevin friction constant
  \item[$\gamma_e$] Electron Langevin friction constant
  \item[$\Gamma$] Bath coupling function
  \item[$\hbar$] Reduced Planck's constant
  \item[$H$] Magnetic field 
  \item[$\mathcal{H}_\textrm{ph}$] Lattice Hamiltonian
  \item[$\mathcal{H}_\textrm{el}$] Electron Hamiltonian
  \item[$\mathcal{H}_\textrm{el}^{\textrm{tb}}$] Electron tight-binding Hamiltonian
  \item[$\bb{I}_{3\times 3}$] $3\times 3$ unit matrix
  \item[$j$] Polarization current
  \item[$k_B$] Boltzmann constant
  \item[$K$] Force constant matrix 
   \item[$\lambda_{\textrm{max}}$] Thermal wavelength
  \item[$\Lambda$] Phonon mean free path
  \item[$L$] System length
  \item[$L_{\textrm{bath}}$] Length of heat bath
   \item[$\mu$] Chemical potential
  \item[$\mu_0$] Vacuum permeability
  \item[$m$] Mass of atom or dipole
  \item[$m_e$] Electron mass
  \item[MD] Molecular dynamics
  \item[$n$] Refractive index
  \item[$N$] Number of atoms
  \item[NEMD] Non-equilibrium molecular dynamics
  \item[$\xi$] Langevin force 
  \item[$\omega$] Angular frequency
  \item[$\omega_0$] Oscillator resonance frequency
  \item[$\omega_r$] Phonon-polariton resonance frequency
    \item[$p$] Dipole moment
  \item[$p^{\textrm{kin}}$] Kinetic momentum  
  \item[$P$] Electric polarization density
  \item[$P_{\textrm{ind}}$] Induced part of electric polarization density
  \item[$P_{\textrm{fluc}}$] Fluctuating part of electric polarization density
  \item[$\phi$] Localized electron eigenstate
  \item[$q$] Dipole charge
  \item[$q(\omega)$] Spectral decomposition of heat current
  \item[$Q$] Heat current
  \item[$Q^{\textrm{bath}}$] Heat current to bath
  \item[$r$] Atom position
  \item[$r_0$] Equilibrium position of atom 
  \item[$R$] Nanoparticle radius
   \item[$\Sigma$] Bath self-energy
  \item[$\sigma$] Electron orbital index
  \item[$S$] Poynting vector
  \item[$t$] Time
  \item[$t_{ij}^{\sigma\sigma'}$] Electron tight-binding hopping constant
  \item[$T$] Temperature
  \item[$T_D$] Debye temperature
  \item[$\mathcal{T}$] Transmission function
  \item[$u$] Displacement of atom from equilibrium position
  \item[$\Upsilon$] Anharmonic force constant
  \item[${V}$] Electron potential energy
  \item[$\mathcal{V}$] Interatomic potential energy function
  \item[$W$] System width
  % \item[$\bu_i$] Vector displacement of atom $i$ 
  \item[$\chi$] Electric susceptibility
\end{description}

\chapter{Introduction}
\setcounter{page}{1}
\pagenumbering{arabic}
\input{intro.tex}

\input{theory.tex}

\chapter{Results and discussion}
\input{results_phonons.tex}

\input{discussion.tex}

\chapter{Conclusion and outlook}

\input{conclusion.tex}

\renewcommand{\bibname}{References}
\bibliographystyle{thesis_style}
%\bibliographystyle{../test}
\bibliography{../bibtex/biblio}{}

%\bibliographystyle{ieeetr}
%\bibliographystyle{../physrev}




\addpublication{K. S\"a\"askilahti, J. Oksanen, J. Tulkki, and S. Volz}{Role of anharmonic phonon scattering in the spectrally decomposed thermal conductance at planar interfaces}{Phys. Rev. B}{90, 134312}{October}{2014}{American Physical Society}{spectral}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author did this and that}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/spectral_article.pdf}

\addpublication{K. S\"a\"askilahti, J. Oksanen, S. Volz, and J. Tulkki}{Frequency-dependent phonon mean free path in carbon nanotubes from nonequilibrium molecular dynamics}{Phys. Rev. B}{91, 115426}{March}{2015}{American Physical Society}{cnt}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author did this and that}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/cnt_article.pdf}


\addpublication{Shiyun Xiong, Yuriy A. Kosevich, K. S\"a\"askilahti, Yuxiang Ni, and Sebastian Volz}{Tunable thermal conductivity in silicon twinning superlattice nanowires}{Phys. Rev. B}{90, 195439}{November}{2014}{American Physical Society}{twinning}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author did this and that}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/twinning_article.pdf}

\addpublication{K. S\"a\"askilahti, J. Oksanen, R.~P. Linna, and J. Tulkki}{Thermal conduction and interface effects in nanoscale Fermi-Pasta-Ulam conductors}{Phys. Rev. E}{86, 031107}{September}{2012}{American Physical Society}{fpu}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
% \addcontribution{The author made the coffee.}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/fpu_article.pdf}

\addpublication{K. S\"a\"askilahti, J. Oksanen, R.~P. Linna, and J. Tulkki}{Phonon interference and anharmonicity effects in nanoconstrictions}{AIP Conf. Proc.}{1506, 15}{December}{2012}{American Physical Society}{fpu2}
% \addcontribution{The author made the coffee.}.
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author made the coffee.}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/fpu_article2b.pdf}

\addpublication{K. S\"a\"askilahti, J. Oksanen, and J. Tulkki}{Thermal balance and quantum heat transport in nanostructures thermalized by local Langevin heat baths}{Phys. Rev. E}{88, 012128}{July}{2013}{American Physical Society}{gf}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author did this and that}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/gf_article.pdf}

\addpublication{K. S\"a\"askilahti, J. Oksanen, and J. Tulkki}{Quantum Langevin equation approach to electromagnetic energy transfer between dielectric bodies in an inhomogeneous environment}{Phys. Rev. B}{89, 134301}{April}{2014}{American Physical Society}{dipole}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
%\addcontribution{The author did this and that}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{articles/dipole_article.pdf}


\end{document}